A Constraint Solving Approach to Parikh Images of Regular Languages

### 2024-03-07 implementation.tex
Fix minor reviewer issues
Closes: #77
Closes: #75
Closes: #76
Closes: #71
Closes: #72
Title case
Example input moved to artefact

\Catra{} is written in Scala, with the calculus described in this paper
implemented as a theory plug-in for the \Princess{} automated theorem
prover~\cite{princess}, which also performs the Presburger reasoning. For
comparison, we also provide an implementation of the baseline method
from~\cite{generate-parikh-image}, a direct translation that uses the~\Nuxmv{}
symbolic model checker~\cite{nuxmv} to solve our constraints, and the
approximation described in~\cite{approximate-parikh} on top of the standard
baseline back-end. An example of an input file corresponding to our running
example introduced in \cref{sec:intuition} can be seen in
\cref{lst:input-example}.

@@

We baseline using the same Presburger solver (\Princess{}), input file parser,
and automaton implementation as \Catra. We do this to better analyse the impact
of the calculus rules themselves. Adapting~\cite{generate-parikh-image}, we
produce quantified Presburger formulae for each successive term and add them to
\Princess. We compute the product incrementally term by term, checking
satisfiability at each step. We use a priority queue to select automata for each
step and order them by their number of transitions. We use this heuristic to put
off computing large (and therefore slow) products until we have to, hoping to
find an empty intermittent product. This is roughly similar to the approach
taken in~\cite{approximate-parikh}.

\begin{algorithm}
  \caption{How we implement the baseline approach}\label{alg:baseline}
  \KwData{$\Automaton_1, \ldots, \Automaton_n$ automata, other constraints $\SomeClause$}
  \KwResult{\textsc{Sat} or \textsc{Unsat}}
  \SetKwFunction{NewTheoremProver}{newTheoremProver}
  \SetKwFunction{NewPriorityQueue}{newPriorityQueue}
  \SetKwFunction{Dequeue}{dequeue}
  \SetKwFunction{Enqueue}{enqueue}
  \SetKwFunction{Assert}{assert}

@@

  $q \gets \NewPriorityQueue{$\mathcal{A}_i, \ldots, \mathcal{A}_n$}$

@@

  \KwRet{$p$'s SAT status}

  \end{algorithm}

@@

\subsection{Heuristics and search strategies}

>>>>

\Catra{} is written in Scala, with the calculus described in this paper
implemented as a theory plug-in for the \Princess{} automated theorem
prover~\cite{princess}, which also performs the Presburger reasoning. For
comparison, we also provide an implementation of the baseline method
from~\cite{generate-parikh-image}, a direct translation that uses the~\Nuxmv{}
symbolic model checker~\cite{nuxmv} to solve our constraints, and the
approximation described in~\cite{approximate-parikh} on top of the standard
baseline back-end. An example of an input file corresponding to our running
example introduced in \cref{sec:intuition} can be found in the root directory
of the artefact~\cref{artefact}.

@@

As a baseline, we use the same Presburger solver (\Princess{}), input file parser,
and automaton implementation as \Catra{}. We do this to better analyse the impact
of the calculus rules themselves. Adapting~\cite{generate-parikh-image}, we
produce quantified Presburger formulae for each successive term and add them to
\Princess{}. We compute the product incrementally term by term, checking
satisfiability at each step. We use a priority queue to select automata for each
step and order them by their number of transitions. We use this heuristic to put
off computing large (and therefore slow) products until we have to, hoping to
find an empty intermittent product. This is roughly similar to the approach
taken in~\cite{approximate-parikh}.

\begin{algorithm}
  \KwData{$\Automaton_1, \ldots, \Automaton_n$ automata, other constraints $\SomeClause$}
  \KwResult{\textsc{Sat} or \textsc{Unsat}}
  \SetKwFunction{NewTheoremProver}{newTheoremProver}
  \SetKwFunction{NewPriorityQueue}{newPriorityQueue}
  \SetKwFunction{Dequeue}{dequeue}
  \SetKwFunction{Enqueue}{enqueue}
  \SetKwFunction{Assert}{assert}

@@

  $q \gets \NewPriorityQueue{$\mathcal{A}_1, \ldots, \mathcal{A}_n$}$

@@

  \KwRet{$p$'s SAT status}
  \caption{How we implement the baseline approach}\label{alg:baseline}
  \end{algorithm}

@@

\subsection{Heuristics and Search Strategies}
